Optimizing Abstract Abstract Machines

### 2012-11-14 paper/paper.tex
Type error in imperative algo. Forgot to pass in empty store changes

\begin{figure}
\begin{alltt}
eval(\(e\)) :=
  \(\msto\), todo, seen, T := \(\varnothing\), \(\varnothing\), [], 0
  \(\compile{e}\)(\(\mtcntr, \varnothing, \varnothing, \kmt\))
  while(true):
    if todo = \(\varnothing\): return (keys(seen), \(\msto\))
    else:
      let old := todo
      todo, \(\msdiff\) := \(\varnothing\), \(\mtlst\)
      foreach c \(\in\) old: \(\changep\) := false; c()
      unless \(\msdiff\) = \(\mtlst\): T += 1; replay!(\(\msdiff, \msto\))
\end{alltt}
\caption{Imperative algorithm}
\label{fig:imperative}
\end{figure}

>>>>

\begin{figure}
\begin{alltt}
eval(\(e\)) :=
  \(\msto\), todo, seen, T := \(\varnothing\), \(\varnothing\), [], 0
  \(\compile{e}\)(\(\mtcntr, \varnothing, \varnothing, \mtlst, \kmt\))
  while(true):
    if todo = \(\varnothing\): return (keys(seen), \(\msto\))
    else:
      let old := todo
      todo, \(\msdiff\) := \(\varnothing\), \(\mtlst\)
      foreach c \(\in\) old: \(\changep\) := false; c()
      unless \(\msdiff\) = \(\mtlst\): T += 1; replay!(\(\msdiff, \msto\))
\end{alltt}
\caption{Imperative algorithm}
\label{fig:imperative}
\end{figure}
